### 2020-08-23 thesis/thesis.tex
[thesis] Ensure all examples are valid Freak programs

\vbox{\begin{verbatim}
    handle
        let fh <- do Open "praise.txt" in
        let c <- do Choice () in
        if c then do Write (fh, "Guy Fieri") else do Write (fh, "is cool");
        do Close fh
    with {
        return x -> [x] |
        Choose _ k -> return (append (k true) (k false)) |
    }
\end{verbatim}
}

>>>>

\vbox{\begin{verbatim}
    handle
        let fh <- do Open "praise.txt" in
        let c <- do Choice () in
        let text <- if c then return "Guy Fieri" else return "is cool" in
        let _ <- do Write (fh, text) in
        do Close fh
    with {
        Choose _ k ->
            let t <- r 1 in
            let f <- r 0 in
            return (t, f) |
        return x -> return x
    }
\end{verbatim}
}
